Transforming Optimal Tetrahelices between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-09 r1doc/TetrahelixUntwistV2.tex
yet another update

%% TODO: Add something about Tetrobots into abstract.
\begin{abstract}
  The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra forming a helical column.  Treating the edges of
  these tetrahedra as structural members creates an attractive and
  inherently rigid space frame, and therefore interesting to architects,
  mechanical engineers, and roboticists.  A formula is developed that matches the
  visually apparent helices forming the outer rails of the BC helix.
  This formula is generalized to a formula convenient to designers.
  Formulae for 
  computing the
  parameters that give proven edge-length minimax-optimal tetrahelices
  are given, defining a continuum of optimum tetrahelices of varying curvature.
  The endpoints of this continuum are the BC helix and
  a structure of zero curvature, the \emph{equitetrabeam}.
 Only one out of three members in the system change their length \highlighttext{ to transform
  the structure into }
  any point in the continuum.
  Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed. 
  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
  A formula for the inradius of optimal tetrahelices is given.
  The continuum allows a regular Tetrobot supporting a length change of less than $16\%$ in the
  BC configuration to untwist into a hexapodal or $n$-podal robot
  to use standard gaits.
\end{abstract}

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in \cref{fig:tetrobot}.

@@

\highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
gives the vertices in space. Eventually, \highlighttext{this would be done}
by choosing the lengths of a small set of members.
In a space frame, this is a static design choice; in a Tetrobot, it is a
dynamic choice that can be used to twist the robot and/or exert linear or
angular force on the environment.

@@

This allows us to redefine:

@@

\begin{proof}
\highlighttext{  
Suppose that all three rails do not have the same pitch.
Let $n1$ be a node on a  shortest edge between
two rails. Let $n2$ be a node on a different rail.
Increasing the difference $\|n2-n1\|$, increasing edge lengths $T(n_1,n_2)$
without bound,
which is not physically realizable.
}

@@

In principle, any three helices generated with \cref{eq:triple}
has at most nine distinct edge length classes. Each edge that connects
two rails potentially has a longer length and shorter length we denote with
a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates),
the interval
defined by the $z$-axis value of its endpoints contains no other vertices,
we call it a \emph{one-hop} edge, and if it does contain another vertex we
call it a \emph{two-hop} edge, as illustrated in \cref{fig:naming}.
Then there are 
3 rail edges $\{ RR, BB, YY\}$,
3 one-hop lengths $\{ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
and 3 two-hop
lengths $\{ RB_{+}, BY_+, RY_+ \}$ between each pair of 3 rails,
where the two-hop length is at least the one-hop length.
However, \highlighttext{generating} the three helices with \cref{eq:triple}
\highlighttext{ will cause }
many of these lengths will be the same.
In fact, it is possible that there
will be only two distinct such classes, and in fact in  the purely regular BC helix there is only one length.

@@

    Any attempt to perturb any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be the edge lengths of such a
    perturbed tetrahelix.
    \highlighttext{The minimax of $R(B)$ is greater than the minimax of $R(A)$} since there is a
    single rail length which cannot be both greater
    than $o'$ and $t'$ and less than $o'$ and $t'$.
    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
    all two-hop edges equal to each other, and the $z$ distances between rails equal. Therefore, vertices are
    $d/3$ from each other on the $z$-axis.
\end{proof}

@@

\begin{proof}
By \cref{thm:eventhirds}, \highlighttext{one} can compute the (at most) three edge-lengths of an optimal
tetrahelix by formulae universally quantified by $n$ and $c$:
\begin{equation}
  \begin{split}
  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r))  \text{ ,} \\
  \end{split}
\end{equation}
\begin{equation}
  \begin{split}  
  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
  \end{split}  
\end{equation}  
  \begin{equation}
  \begin{split}    
  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
  \end{split}  
\end{equation}

@@

Since the axes are parallel, may define the \emph{inradius}, represented by the letter $i$, of a
tetrahelix to be the radius of the largest
cylinder parallel to this axis that is surrounded by each tetrahelix and penetrated by no edge.

>>>>

%% TODO: Add something about Tetrobots into abstract.
\begin{abstract}
  The Boerdijk-Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra forming a helical column.  Treating the edges of
  these tetrahedra as structural members creates an attractive and
  inherently rigid space frame, and therefore is interesting to architects,
  mechanical engineers, and roboticists.  A formula is developed that matches the
  visually apparent helices forming the outer rails of the BC helix.
  This formula is generalized to a formula convenient to designers.
  Formulae for 
  computing the
  parameters that give proven edge-length minimax-optimal tetrahelices
  are given,
  \highlighttext{
  allowing transformation through a continnum of 
  of optimum tetrahelices of varying curvature while maximizing regularity.}
  The endpoints of this continuum are the BC helix and
  a structure of zero curvature, the \emph{equitetrabeam}.
 Only one out of three members in the system change their length \highlighttext{ to transform
  the structure into }
  any point in the continuum.
  Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed. 
  An interactive tool for such design and experimentation is provided: \url{https://pubinv.github.io/tetrahelix/}.
  A formula for the inradius of optimal tetrahelices is given.
  The continuum allows a regular Tetrobot supporting a length change of less than $16\%$ in the
  BC configuration to untwist into a hexapodal or $n$-podal robot
  to use standard gaits.
\end{abstract}

@@

Imagining \cref{fig:closeup} or \cref{fig:closeuporthog} as a static mechanical structure,
observe that it is useful to the mechanical engineer
because the structure is a mechanically strong, inherently rigid,
omni-triangulated space frame.
Then imagine that each static edge is replaced with an
actuator that can dynamically become shorter or longer in response to electronic control,
and the vertices are joints that support sufficient angular displacement
for this to be possible. An example of such a machine is a Tetrobot,
shown in figs. [4] and \cref{fig:tetrobot}.

@@

\highlighttext{Engineers} would like to design nearly regular tetrahelices with a formula that
gives the vertices in space. Ideally, \highlighttext{this would be done}
by choosing the lengths of a small set of members.
In a space frame, this is a static design choice; in a Tetrobot, it is a
dynamic choice that can be used to twist the robot and/or exert linear or
angular force on the environment.

@@

This \highlighttext{allows \cref{eq:colored} to be rewritten}:

@@

\begin{proof}
\highlighttext{  
Suppose that all three rails do not have the same pitch.
Let $n_1$ be a node on a  shortest edge between
two rails. Let $n_2$ be a node on a different rail.
Increasing the difference $\|n_2-n_1\|$ increases edge lengths $T(n_1,n_2)$
without bound,
which is not physically realizable.
}

@@

In principle, any three helices generated with \cref{eq:triple}
has at most nine distinct edge length classes. Each edge that connects
two rails potentially has a longer length and shorter length we denote with
a $+$ or $-$. So the classes are $\{ RR, BB, YY, RB_+, RB_-, BY_+, BY_-, RY_+, RY_- \}$.
If when projecting all vertices onto the $z$-axis (dropping the $x$ and $y$ coordinates),
the interval
defined by the $z$-axis value of its endpoints contains no other vertices,
we call it a \emph{one-hop} edge, and if it does contain another vertex we
call it a \emph{two-hop} edge, as illustrated in \cref{fig:naming}.
Then there are 
3 rail edges $\{ RR, BB, YY\}$,
3 one-hop lengths $\{ RB_-, BY_-, RY_- \}$ between each pair of 3 rails,
and 3 two-hop
lengths $\{ RB_{+}, BY_+, RY_+ \}$ between each pair of 3 rails,
where the two-hop length is at least the one-hop length.
However, \highlighttext{generating} the three helices with \cref{eq:triple}
\highlighttext{ will cause }
many of these lengths to be the same.
In fact, it is possible that there
will be only two distinct such classes, and in fact in  the purely regular BC helix there is only one length.

@@

    Any attempt to perturb any rail in either $z$ direction lengthens one two-hop edge to $t'$, where $t' > t$
    and shortens one one-hop edge $o' < o$. Let $B = \{o',t' \} \cup A$ be the edge lengths of such a
    perturbed tetrahelix.
    \highlighttext{The minimax of $B$ is greater than the minimax of $A$: $R(B) > R(A) $} since there is a
    single rail length which cannot be both greater
    than $o'$ and $t'$ and less than $o'$ and $t'$.
    Therefore, any optimal tetrahelix has all one-hop edges between all rails equal to each other, and
    all two-hop edges equal to each other, and the $z$ distances between rails equal. Therefore, vertices are
    $d/3$ from each other on the $z$-axis.
\end{proof}

@@

\begin{proof}
By \cref{thm:eventhirds}, \highlighttext{one} can compute the (at most) three edge-lengths of an optimal
tetrahelix by formulae universally quantified by $n$ and $c$:
\begin{equation}
  \begin{split}
  1 = \text{rail} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n+1,c,\rho,d_{\rho}),r)) || \text{ ,} \\
  \end{split}
\end{equation}
\begin{equation}
  \begin{split}  
  \text{one-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n,c+1,\rho,d_{\rho},r)) || \text{ and,} \\
  \end{split}  
\end{equation}  
  \begin{equation}
  \begin{split}    
  \text{two-hop} &= || \vec{H}_{general}(n,c,\rho,d_{\rho},r)  - \\
  &  \vec{H}_{general}(n,c+2,\rho,d_{\rho},r)) || \text{ .}\\
  \end{split}  
\end{equation}

@@

Since the axes are parallel, one may define the \emph{inradius}, represented by the letter $i$, of a
tetrahelix to be the radius of the largest
cylinder parallel to this axis that is surrounded by each tetrahelix and penetrated by no edge.
